With Great Growth, Comes Greater Consumption: Energy Consumption of Countries Around the world in Relation to Their annual GDP growth

### 2024-04-22 paper/paper.qmd
Added figures to papers

- **Normality**: We assume the residuals of the regression, \( \epsilon_{it} \), are normally distributed, facilitating the use of classical statistical tests for hypothesis testing (e.g., t-tests for coefficients).
- **Independence**: Observations across years and countries are assumed to be independent of each other.
- **Homoscedasticity**: The error terms are assumed to have constant variance across different levels of energy consumption.
- **Linearity**: The relationship between GDP growth and energy consumption is presumed to be linear after appropriate transformations if required (e.g., logarithmic).
# Results

@@

```{r, fig.cap = "Total GDP Growth of all copuntries Over Time 1992-2022", tab.width=5, echo=FALSE}
#| warning: false
#| message: false

ggplot(countries_energy_GDP_data, aes(x = Year, y = Average_GDP_Growth)) +
  geom_point(color="orange") +
  labs(title = "Average GDP Growth Over Time for High Income Countries",
       x = "Year",
       y = "GDP Growth (%)",
       caption = "Data source: Your data source") +
  theme_minimal()

@@

@@

@@

@@

>>>>

- **Normality**: We assume the residuals of the regression, \( \epsilon_{it} \), are normally distributed, facilitating the use of classical statistical tests for hypothesis testing (e.g., t-tests for coefficients).
- **Independence**: Observations across years and countries are assumed to be independent of each other.
- **Homoscedasticity**: The error terms are assumed to have constant variance across different levels of energy consumption.
- **Linearity**: The relationship between GDP growth and energy consumption is presumed to be linear after appropriate transformations if required (e.g., logarithmic).

# Results

@@

These two graphs depict the trends in global economic activity and energy usage. The first graph shows how average GDP growth has changed over time, offering insights into economic trends. The second graph illustrates the total energy consumption across different income levels from 1992 to 2022, showing how economic status influences energy usage patterns.

```{r, fig.cap = "Total GDP Growth of all countries Over Time 1992-2022", tab.width=5, echo=FALSE}
#| warning: false
#| message: false

ggplot(countries_energy_GDP_data, aes(x = Year, y = Average_GDP_Growth)) +
  geom_point(color="orange") +
  labs(title = "Average GDP Growth Over Time for All Countries",
       x = "Year",
       y = "GDP Growth (%)",
       caption = "Data source: World Bank National Accounts Data") +
  theme_minimal()

@@

**Comparison of Observed Data and Model Predictions: Posterior Predictive Check**

![](../figures/mcmc_trace_plot.png)

**Figure** *Markov Chain Monte Carlo (MCMC) trace plots for the Bayesian linear regression model parameters. The left panel displays the trace for the model's intercept, and the right panel shows the trace for the coefficient of Log_Energy_Consumption. Each plot contains four overlaid chains (Chain 1 to Chain 4), illustrated in different shades of blue. The trace plots illustrate the sampling path of the chains through the parameter space over 1000 iterations post warm-up. The plots exhibit stable convergence and adequate mixing of the chains, suggesting that the sampling process has reached equilibrium and that the posterior distributions are well-estimated.*

@@

**Comparison of Observed Data and Model Predictions: Posterior Predictive Check**

![](../figures/pp_check_plot.png)

**Figure** *Posterior predictive check plot comparing the observed values of the outcome variable (y, in dark blue) to the replicated data (yrep, in light blue) generated from the model's posterior distribution. The sharp peak and significant overlap between the observed and replicated distributions around the zero mark demonstrate that the model's predictions closely align with the observed data, indicating an adequate fit for the central tendency of the data. The tails of the distribution should be examined for potential discrepancies between observed and predicted values.*

@@

**Posterior Distributions and Parameter Correlation for Bayesian Model of Energy Consumption and GDP Growth **

![](../figures/pairs_plot.png)
**Figure** *Pairs plot depicting the posterior distributions and bivariate relationships of the Bayesian linear regression model parameters. The diagonal panels show the density plots of the intercept (top left) and Log_Energy_Consumption (bottom right), both illustrating the posterior distribution of these parameters, which are unimodal and symmetric, suggesting precise estimates. The off-diagonal panels depict the scatterplot between the intercept and Log_Energy_Consumption with a fitted regression line, indicating a negligible correlation between the parameters, as shown by the horizontal trend of the fitted line and the even spread of points around it.*

@@

**Residual Analysis of GDP Growth Predictions from Energy Consumption Model **

![](../figures/residuals_plot.png)
**Figure** *Scatter plot of the residuals from the Bayesian linear regression model. The residuals (the differences between observed and predicted values of Average GDP Growth) are plotted against the predicted values. The concentration of points around the horizontal axis (residuals of zero) indicates that the model generally fits the data well. However, the presence of points distant from the horizontal axis reflects outliers or instances where the model has significant predictive errors, suggesting areas where model assumptions may not hold or where further model refinement is necessary.*
